Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-04-23 tex/paper1/paper1.tex
edits to the paper

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
\ln P_{1}(f) = \ln P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus the second term,
modelling the excess power.

@@

\section{Posterior predictive checking}

>>>>

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of uncorrelated and incoherent Fourier power.  This suggests that a
second model for these regions should be considered.  The spectrum
$P_{1}$ where
\begin{equation}
\label{eq:pwrlawbunp}
P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
\end{equation}
contains the previous power law dependence, plus a second term which
models any power over and above the power law.

@@

\section{Determining the number of independent
  measurements}\label{sec:app:ind}

Figures \ref{} show that the logarithm of the Fourier power in a
region of the Sun may be approximated by a normal distribution $N(\mu,
\sigma)$.  The
maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}
